Crowd density estimation from Wi-Fi positioning data in the Amsterdam Arena

### 2016-07-07 PaperOnSmoothing/draft-31052016.tex
One or two revisions on Methods section.

\begin{equation}
\text{d}X(t)=\sigma\text{d}W(t)
\end{equation}
where $W(t)$ is a Wiener process. The density function $f(t,x)$ of the displacement of $X$ in the time interval $[0,t]$ is known, and is a normal distribution with mean $X(0)$ and variance
\begin{equation}
\text{Var(\textit{X(t)})}=\sigma^{2}t
\end{equation}
Thus, in case we have no new observations, we smooth the density estimate from the previous epoch by convolution with the normal density function. 
The variance is determined by the length $t$ of the time interval, and the walking speed of pedestrians. 
[Optional: We relate $\sigma$ to the walking speed of pedestrians by setting $\sigma^2=2Dt$, where ]
\begin{equation}
D=\frac{(\Delta X)^2}{2\Delta t}
\end{equation}
The walking speed can be related to the local crowd density via the so-called \textit{Fundamental Diagram}. 
When the density increases the movement of pedestrians becomes more impeded.
The fundamental diagram has been the subject of extensive study [examples].
Here we use the fundamental diagram as provided by ... [?]

Smoothing a two-dimensional (input) function by convolution with a Gaussian weight function that adapts its width to the local values of the input function is [complicated and] time-consuming.\\

>>>>

\begin{equation}
\text{d}X(t)=\sigma\text{d}W(t)
\end{equation}
where $W(t)$ is a Wiener process. The density function $f(t,x)$ of the displacement of $X$ in the time interval $[0,t]$ is known, and is a normal distribution with mean $X(0)$ and variance
\begin{equation}
\text{Var(\textit{X(t)})}=\sigma^{2}t
\end{equation}
Thus, in case we have no new observations, we smooth the density estimate from the previous epoch by convolution with the normal density function. 
The variance is determined by the length $t$ of the time interval, and the walking speed of pedestrians.
[Optional: We relate $\sigma^2$ to the walking speed of pedestrians as defined by]
\begin{equation}
\sigma^2=\frac{(\Delta X)^2}{\Delta t}
\end{equation}
The walking speed of pedestrians can be related to the local crowd density via the so-called \textit{Fundamental Diagram}. 
The fundamental diagram generally states that walking speed of pedestrians is a decreasing function of the local crowd density [(Weidman 1992)].
The fundamental diagram function has been the subject of extensive study [examples].
Although all these studies agree on the decreasing form of the function, empirical studies in different countries and cultures have resulted in different forms and parameters values.

Here we use the fundamental diagram as provided by ... [?]
